Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-05-07 manuscripts/manuscript.Rmd
avoid nasty dplyr nonstandard eval problem

ggplot(filter(table1_long, reduction == reduction),
  aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  scale_fill_discrete(name="error type") + 
  scale_x_discrete(labels = c('L1' = substitute(paste(Pi[1])),
                              'L2' = substitute(paste(Pi[2])),
                              'fixed' = substitute(paste(Pi[3])))) + 
  xlab("Cost model") + 
  ylab(expression(NPV[0])) + theme_tufte(base_size=16)
write.csv(table1_long, "components/data/figure6.csv")
```

>>>>

ggplot(filter(table1_long, reduction == 0.25),
  aes(penalty.fn, value, fill = variable)) + 
  geom_bar(stat="identity", position="dodge") + 
  scale_fill_discrete(name="error type") + 
  scale_x_discrete(labels = c('L1' = substitute(paste(Pi[1])),
                              'L2' = substitute(paste(Pi[2])),
                              'fixed' = substitute(paste(Pi[3])))) + 
  xlab("Cost model") + 
  ylab(expression(NPV[0])) + theme_tufte(base_size=16)
write.csv(table1_long, "components/data/figure6.csv")
```
